A Tool for the Range Analysis of Whole Programs

### 2012-05-09 doc/Manuscript/DTool/paper.tex
Changed the example a little bit.

\title{A Tool for Range Analysis of Whole Programs}

@@

% The demo tool.
\noindent
\textbf{Software: }
Our tool is publicly available for
download at \texttt{http://code.google.com/p/range-analysis/}.
In our webpage we provide, in addition to the static range analysis itself,
a profiler that records the minimum and maximum values assigned to each
variable during program execution.
We also provide a visual interface to our tool, which lets the user to
see the control flow graph of the target program.
This visual interface also lets the user to see the integer intervals that
the analysis estimates to each variable.

@@

This sequence of calls will cause our example pass to be dynamically loaded
by the LLVM framework.
It will receive the bitcodes that we had produced before, and will produce,
as output, a list of variables, followed by their intervals.

>>>>

\title{A Tool for the Range Analysis of Whole Programs}

@@

% The demo tool.
\noindent
\textbf{Software: }
Our tool is publicly available for
download at \texttt{http://code.google.} \texttt{com/p/range-analysis/}.
In our webpage we provide, in addition to the static range analysis itself,
a profiler that records the minimum and maximum values assigned to each
variable during program execution.
We also provide a visual interface to our tool, which lets the user to
see the control flow graph of the target program.
This visual interface also lets the user to see the integer intervals that
the analysis estimates to each variable.

@@

This sequence of calls will cause our example pass to be dynamically loaded
by the LLVM framework.
It will receive the bitcodes that we had produced before, and will produce,
as output, a list of variables, followed by their intervals.
Below we have the output that our analysis prints for the input program in Figure~\ref{fig:overall_view}(a).
%Example pass: Source code
\begin{lstlisting}[frame=single]
Cousot Intra Procedural analysis (Values -> Ranges) of foo:
[0, 100]  %k.0 = phi i32 [ 0, %bb ], [ %tmp9, %bb8 ]
[0, 99]  %vSSA_sigma = phi i32 [ %k.0, %bb1 ]
[-1, 99]  %j.0 = phi i32 [ %vSSA_sigma, %bb2 ], [ %tmp7, %bb5 ]
[0, 99]  %i.0 = phi i32 [ 0, %bb2 ], [ %tmp6, %bb5 ]
[0, 99]  %vSSA_sigma3 = phi i32 [ %j.0, %bb3 ]
[0, 98]  %vSSA_sigma2 = phi i32 [ %i.0, %bb3 ]
[1, 99]  %tmp6 = add nsw i32 %vSSA_sigma2, 1
[-1, 98]  %tmp7 = sub nsw i32 %vSSA_sigma3, 1
[1, 100]  %tmp9 = add nsw i32 %vSSA_sigma, 1
[100, 100]  %vSSA_sigma1 = phi i32 [ %k.0, %bb1 ]

Cousot Intra Procedural analysis (Values -> Ranges) of main:
\end{lstlisting}
Notice that we get a number of output lines for function \texttt{foo}, and zero
for function \texttt{main}.
Each output line is the range of a given variable, using LLVM's internal
representation.
It is important to use the \texttt{instnamer} pass, like we did before, to get
some meaningful names for the variables.
We did not get any line for \texttt{main} just because this function did not have
any variable with a known range.
